---
title: "README"
author: "Zachary McCaw"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: TRUE
--- 

# Compute Winner's Curse Correction

Zachary McCaw <br>
Updated: 20-09-15

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

### Description

This package calculates the winner's curse correction using the model proposed by [Turley *et al* (2018)](https://pubmed.ncbi.nlm.nih.gov/29292387/), implemented via the Expectation-Maximization algorithm. Also see [MGMM](https://github.com/zrmacc/MGMM) for fitting Gaussian Mixture Models more generally. 

## Installation

```{R, eval=FALSE}
devtools::install_github(repo = 'zrmacc/WinCurse')
```

## Model
This package fits the following hierarchical model:
$$
Z_{i} \sim \text{Bern}(\pi) \\
\theta_{i}|(Z_{i}=1) \sim \delta_{0} \\
\theta_{i}|(Z_{i}=0) \sim N(0, \tau^{2}) \\
\hat{\theta}_{i}|\theta_{i} \sim N(\theta_{i}, \sigma_{i}^{2})
$$

where $\pi$ is the probability of the null component, $\delta_{0}$ is a point-mass on zero, $\tau^{2}$ is a variance component for the non-null parameters, $\theta_{i}$ is the true underlying parameter, $\hat{\theta}_{i}$ is the corresponding estimate, and $\sigma_{i}^{2}$ is the sampling variance, assumed known. 

## Examples

### Data

Example may be loaded via:

```{R}
library(WinCurse)
data(wc_data)
head(wc_data)
```

Here: 

* `non_null` is the generative component, 1 if non-null, 0 if null. 
* `theta` is the estimated parameter. 
* `se` is the standard error of the estimated parameter. 

The true $\pi = 0.75$ and the true $\tau^{2} = 0.05$. 

### Estimation

To fit the winner's curse model: 
```{r}
set.seed(100)
fit <- fit.WinCurse(
  theta = wc_data$theta,
  se = wc_data$se,
  pi = 0.5,
  tau2 = 1,
  eps = 1e-12
)
show(fit)
```

#### Outputs

The output of `fit.WinCurse` is an object of class `winCurse` with these slots.

* `@Assignments` containing the component assignments and assignment entropy. Higher entropy means the assignment is less certain. 

```{r}
head(fit@Assignments)
```

* `@Estimates` containing the parameter estimates:

```{r}
fit@Estimates
```

* `@Expectations` containing the posterior expectation of $\theta_{i}$ given $\hat{\theta}_{i}$, which is shrunk towards zero. 

```{r}
head(fit@Expectations)
```
* `@Responsibilities` containing the posterior membership probabilities to the null and non-null components. 

```{r}
head(fit@Responsibilities)
```
