---
title: "WinCurse: Winner's Curse Correction"
author: "Zachary McCaw"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{WinCurse: Winner's Curse Correction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

**WinCurse** implements winner's curse correction using the two-component mixture model of Turley *et al.* (2018), fitted by the Expectation-Maximization (EM) algorithm.

**Model.** For each of $n$ independent effect sizes $(\theta_{1}, \dots, \theta_{n})$, we observe an estimate $\hat{\theta}_{i}$ and corresponding standard error $\sigma_{i}$. With probability $\pi$, the true effect is exactly zero, and with probability $1 - \pi$ the true effect is drawn from a normal distribution with mean zero and variance $\tau^2$ (non-null). The estimated effect size $\hat{\theta}_{i}$ is normally distributed about the true effect size $\theta_{i}$ with variance $\sigma_{i}^{2}$:

$$
\hat{\theta}_{i} | \theta_{i} \sim N(\theta_{i}, \sigma_{i}^{2})
$$
Marginally, $\hat{\theta}_{i}$ is drawn from a mixture of two normals:

$$
\hat{\theta}_{i} \sim \pi \cdot N(0, \sigma_{i}^{2}) + (1 - \pi) \cdot N(0, \tau^{2} + \sigma_{i}^{2})
$$

The package estimates $\pi$ and $\tau^2$ by maximum likelihood via the EM algorithm. It then computes:

* The maximum *a posteriori* component assignment (i.e. null vs non-null).

* The posterior probabilities of belonging to the null and non-null components.

* The posterior expected effect size $\mathbb{E}(\theta_{i} | \hat{\theta}_{i})$. 


## Quick start

Load the package and example data:

```{r}
library(WinCurse)
data(wc_data)
```

The data contain effect estimates (`theta`), standard errors (`se`), and the true generative component (`non_null`). Fit the model with `fit.WinCurse`:

```{r}
fit <- fit.WinCurse(
  theta = wc_data$theta,
  se = wc_data$se
)
show(fit)
```

## Outputs

The fitted object has slots:

- **Estimates**: `pi` (null proportion) and `tau2` (non-null variance).

```{r}
fit@Estimates
```

- **Assignments**: maximum a posteriori component and assignment entropy.

```{r}
head(fit@Assignments)
```

- **Expectations**: posterior expected effect sizes (shrunk toward zero).

```{r}
head(fit@Expectations)
```

- **Responsibilities**: posterior probabilities of null vs non-null.

```{r}
head(fit@Responsibilities)
```

## Posterior calculations only

For pre-specified $\pi$ and $\tau^2$, use `PostExp` to compute posterior expectations without fitting:

```{r}
post_exp <- PostExp(
  theta = wc_data$theta,
  se = wc_data$se,
  pi = 0.75,
  tau2 = 0.05
)
```

